---
title: "Reproducible Research Project 1"
author: marcin1213
output: html_document
 
---

`{r} time`

##Loading and preprocessing the data


Read data:
```{r}
st <- read.csv("C:/Users/Marcin/Desktop/R/repdata-data-activity/activity.csv", header = TRUE)
```

Filter out NA values:
```{r}
st_cl <- st[!is.na(st$steps),]
```

Aggregate by date and name columns:
```{r}
st_cl_agr <- aggregate(st_cl$steps, by = list(st_cl$date), FUN = "sum" )
names(st_cl_agr) <- c("date","steps")
```

##What is mean total number of steps taken per day?



```{r}
hist(st_cl_agr$steps, xlab="Number of steps", main = "Histogram: Number of steps")
```


```{r}
aMean <- mean(st_cl_agr$steps)
```


```{r}
aMedian <- median(st_cl_agr$steps)
```

Mean is `r aMean` , median is `r aMedian`

##What is the average daily activity pattern?

Aggregate by interval and name columns:
```{r}
st_cl_agr2 <- aggregate(st_cl$steps, by = list(st_cl$interval) , FUN = "mean" )
names(st_cl_agr2) <- c("interval","steps")
```

```{r}
with(st_cl_agr2, plot(interval, steps, type = "l", main = "Sum of steps taken every day"))
```

```{r}
paste("The highest value of interval: [", st_cl_agr2[which.max(st_cl_agr2$steps),2], "] for interval [", st_cl_agr2[which.max(st_cl_agr2$steps),1],"]")
```

##Imputing missing values

```{r}
NAcount <- length(which(is.na(st$steps)))
```

Count of missing values is [`r NAcount`]

I choose MEAN values of all steps (skipping NA values) to impute missing values,

```{r}
st_steps_NA <-  which(is.na(st$steps))
st_steps_Mean <- mean(st[which(!is.na(st$steps)),"steps"] )
st[st_steps_NA,"steps"]  <- st_steps_Mean
st_agr <- aggregate(st$steps, by = list(st$date), FUN = "sum" )
names(st_agr) <- c("date","steps")
hist(st_agr$steps, xlab="Number of steps", main = "Histogram: Number of steps (NA values replaced with mean)")
a1Mean <- mean(st_agr$steps)
a1Median <- median(st_agr$steps)
```

```{r, echo=FALSE}
medianDiff = abs(aMedian - a1Median) / aMedian * 100
meanDiff = abs(aMean - a1Mean) / aMean * 100
```


New mean is `r a1Mean`  and new median is `r a1Median`
what gives difference for median `r medianDiff`% and difference for mean `r meanDiff`%.



##Are there differences in activity patterns between weekdays and weekends?

```{r, echo = FALSE}
library(ggplot2)
```

```{r}
library(ggplot2)
st$wDay <- ifelse(weekdays(as.Date(st$date)) == c('Samstag','Sonntag'), 'weekend','weekday')
st_agr_wDay <- aggregate(st$steps, by = list(st$interval, st$wDay), FUN = "sum" )
names(st_agr_wDay) <- c("interval","WeekDay_Type","steps")
with(st_agr_wDay, qplot(interval, steps, col = WeekDay_Type, geom = "line"))
```


